Log Journal Project Theme 9

### 2022-10-24 Resources/LogJournal.Rmd
Finished the logjournal

```{r}
# Create a cor matrix
cor_matrix <- cor(data[, -c(5,9)])
cor_matrix <- as_tibble(cor_matrix)
# Add a column with the varibale names
(cor_matrix <- cor_matrix %>% mutate(varnames = all_of(attr_names)[-c(1,6,10)]))
```

@@

```{r}
# Create a long matrix
(cor_matrix_long <- pivot_longer(data = cor_matrix, 
                                 cols = all_of(attr_names)[-c(1,6,10)], 
                                 names_to = "variable", values_to = "cor"))
```

@@

*Criteria for MIL algorithms*

@@

ggplot(data=res, aes(x=Key_Scheme, y=Area_under_ROC, fill=Key_Scheme)) + 
  geom_bar(stat="identity") + 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) + 
  labs(x="Classifier", y="Area under curve (ROC)", 
       title="Area under the curve for different classifiers") + 
  geom_hline(aes(yintercept=min(Area_under_ROC)), linetype = 'dashed') + 
  geom_hline(aes(yintercept=max(Area_under_ROC)), linetype = 'dashed') + 
  geom_text(aes(label=round(Area_under_ROC, digits=2)), vjust=-0.3, size=3.5)
```

@@

ggplot(data=res, aes(x=Key_Scheme, y=IR_precision, fill=Key_Scheme)) + 
  geom_bar(stat="identity") + 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) + 
  labs(x="Classifier", y="Precision", 
       title="Average precisionfor different classifiers") + 
  geom_hline(aes(yintercept=min(IR_precision)), linetype = 'dashed') + 
  geom_hline(aes(yintercept=max(IR_precision)), linetype = 'dashed') + 
  geom_text(aes(label=round(IR_precision, digits=2)), vjust=-0.3, size=3.5)
```

@@

As it can be seen in this table, RandomForest with tweaked parameters is the best. This one has no ? at VAC and precision.

>>>>

```{r, warning=FALSE}
# Create a cor matrix
cor_matrix <- cor(data[, -c(5,9)])
cor_matrix <- as_tibble(cor_matrix)
# Add a column with the varibale names
cor_matrix <- cor_matrix %>% mutate(varnames = all_of(attr_names)[-c(1,6,10)])
kbl(cor_matrix, booktabs = T, align = "c") %>%
  kable_styling(full_width = T)
```

@@

```{r, warning=FALSE}
# Create a long matrix
cols <- all_of(attr_names)[-c(1,6,10)]
cor_matrix_long <- pivot_longer(data = cor_matrix, 
                                 cols = cols,
                                 names_to = "variable", values_to = "cor")
pander(head(cor_matrix_long))
```

@@

**Criteria for MIL algorithms**

@@

ggplot(data=res, aes(x=Key_Scheme, y=Area_under_ROC, fill=Key_Scheme)) + 
  geom_bar(stat="identity") + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  labs(x="Classifier", y="Area under curve (ROC)", 
       title="Area under the curve for different classifiers") + 
  geom_hline(aes(yintercept=min(Area_under_ROC)), linetype = 'dashed') + 
  geom_hline(aes(yintercept=max(Area_under_ROC)), linetype = 'dashed') + 
  geom_text(aes(label=round(Area_under_ROC, digits=2)), vjust=1.5, size=3.5)
```

@@

ggplot(data=res, aes(x=Key_Scheme, y=IR_precision, fill=Key_Scheme)) + 
  geom_bar(stat="identity") + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  labs(x="Classifier", y="Precision", 
       title="Average precision for different classifiers") + 
  geom_hline(aes(yintercept=min(IR_precision)), linetype = 'dashed') + 
  geom_hline(aes(yintercept=max(IR_precision)), linetype = 'dashed') + 
  geom_text(aes(label=round(IR_precision, digits=2)), vjust=1.5, size=3.5)
```

@@

As it can be seen in this table, RandomForest with tweaked parameters is the best. This one has no '?' at VAC and precision.
